\section{Background}
\label{sec:background}
The DIP given by this mauve paper referred  lots of related works and also extended our previous results. Here we introduce the related works, which play a significant role for the  reference and guidance of this mauve paper.

\subsection{DApp's Developer Incentive}
As far as we know, currently, no decentralized platform on blockchain offers a long-term effective incentive mechanism for DApp developers. As a representation of blockchain 2.0, Ethereum makes a breakthrough to involve turing-complete smart contracts. A number of DApps emerge on Ethereum, including game, gambling, crowd sourcing, credit and many other types. In particular, the CryptoKitties in the late 2017 and Fomo 3D in 2018 attract most attentions, which once cause network congestions.

<<<<<<< HEAD
Actually, like the two famous DApps, most DApps gain utilities only by charging fees to users, unable to benefit from the increment of Ethereum's value or the rewards for new blocks. 
=======
>>>>>>> 3f5487d54431522b2d7e898831b15c6b53045955

With the lack of the incentive of developer, the application scenarios of DApps
has also been affected to a certain extent. For example, implicitly, free DApps
may be absence due to the difficulty for getting a return. As a result, the
quantity, quality and diversity of DApps are affected. In contrast, a fair and
effective mechanism for incentivizing developers brings developers'
concentration to the development of DApps, which further promotes the prosperity and sustainable development of the whole blockchain ecosystem.

To a certain extent, many emerging blockchain systems realize the necessity of incentive mechanism for building blockchain ecosystems. For example, in Nebulas Incentive Program, more than 6781 DApps have been generated and a large number of excellent development teams can go to the front desk and obtain high investments.

Along with it, other public blockchains also launched short-term incentive programs based on centralized management. Such incentive programs mainly aims to publicize to the community with official evaluations taking a major role, without long-term sustainability.


\subsection{Nebulas Rank}
Nebulas Rank (NR)~\cite{Nebulasyellowpaper} quantifies each account's contribution to the total economic output and has nice properties against manipulations. In particular, Nebulas Rank introduces the Wilbur function, which has the following properties:

\begin{property}
	\label{prop:one}
	For any two positive variables $x_1$,$x_2$, the sum of their functions is less than the function of their sum.
	%对于任意输入$x$，将其拆分后的计算函数之和小于原计算函数。
\end{property}
\begin{align}
	f(x_1+x_2)>f(x_1)+f(x_2) \quad x_1>0,x_2>0
\end{align}
\begin{property}
	\label{prop:two}
	For any two positive variables $x_1$,$x_2$, when they tend to infinity, the sum of their functions tends to the function of their sum.
\end{property}

\begin{align}
	\lim\limits_{x_1 \to \infty, x_2\to \infty} f(x_1+x_2) = f(x_1) + f(x_2)\quad x_1>0, x_2>0
\end{align}
\noindent As the basis of NR, the two properties also offer nice properties for DIP against manipulations.

\subsection{Voting Mechanism}
As mentioned earlier, in DIP, the process that users use DApps can be regarded as a process that voters vote for DApps. The later's incentive mechanism is similar to ranking algorithms.

About voting mechanism and ranking algorithm, there are lots of related work in various fields, which we have referred and show examples as follows.

One of the most famous results is the Arrow's Theorem, which shows that no ranking algorithm can simultaneously satisfy Pareto Efficiency, i.e., the ranking results satisfies the majority's interest, non-dictatorship and independent of irrelevant alternatives, i.e. the relative ranking of two candidates is not affected by any third candidate.

The result implies that no ranking algorithm can cover everything. So the DIP
in this mauve paper will focus on the important and well-known attributes.

In the real life, there are a lot of scenarios requiring ranking algorithms. A
typical and related example is the buyers' impressions to sellers (merchant) on
Amazon and Taobao. Sellers with higher reputations will be given better display
slots thus obtain more attentions and higher click-through rates (CTRs). In
particular, there are similar problems on such e-commerce platforms, like Sybil attack, i.e., creating fake transactions or buy over buyers to obtain 5-star evaluations.

For now, these centralized platforms mostly rely on machine learning to
distinguish normal and fake
users~\cite{mukherjee2013spotting,jindal2008opinion,yoo2009comparison}.
However, practical results show that such methods are not ideal.
~\cite{ott2011finding} points out that even artificial identifications can not
effectively distinguish such accounts. ~\cite{cai2016mechanism} gives an
algorithm that eliminates the incentive of such manipulations, based on
mechanism design. Although its model is different form us, it can be used as a significant reference.

~\cite{salihefendic2010hacker} introduces the ranking algorithm for postings in
a social network community, which combines the users' votes and time declining. ~\cite{salihefendic2010reddit} introduces the ranking algorithm for postings in Reddit, which involves the situation where users can vote in the negative.
~\cite{miller2009how} introduced Reddit's ranking algorithm for the comments, taking the confidence interval into account.
IMDB ~\cite {IMDB} introduces the idea of Bayesian Model Averaging to film
rankings, which can narrow the gap among different films due to the number of voters.

Because of properties against manipulation in NR, the DIP proposed in this mauve paper can distinguish normal users and fake users more clearly. Therefore, the emphasis of this mauve paper is to transfer users' NR values to DApps' ranking scores through interactive behaviors.


